Estimating the incidence of SARS-CoV-2 from prevalence data

### 2023-09-27 incidence-prevalence.tex
Rearrange chapter

\section{Incidence, prevalence, and duration}

@@

@@

\section{Prevalence data}

@@

\emph{Backcalculation} is a procedure that combines the elements of the previous two sections to estimate incidence based on a measurement of prevalence

>>>>

\section{Definitions}

@@

\emph{Backcalculation} is the procedure for estimating incidence based on a measurement of prevalence.
It was first developed in the context of HIV (human immunodeficiency virus) and AIDS (acquired immune deficiency syndrome)~\autocite{brookmeyerMethod}.
HIV is a virus transmitted sexually or through blood, and causes the disease AIDS.
AIDS has killed around 40 million people; at its peak, around 2 million people died from AIDS each year\todo{cite WHO}.
In this context, backcalculation estimates the incidence of HIV infection from data on the number of AIDS diagnoses and the distribution of the time between infection and AIDS diagnosis~\autocite{brookmeyerBackcalculation}{brookmeyerMeasuring}.
\todo{explain how AIDS diagnosis is "prevalence" data (is it?)}

Two processes are involved in backcalculation: the \emph{prevalence process} and the \emph{observation process}.
The prevalence process describes the relationship between incidence and prevalence.
The observation process describes the relationship between prevalence and the observed data.

\section{Prevalence process}

@@

\section{Observation process}

@@
